A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-11-02 sections/healthcare_application/main.tex
Add introduction and conclusion sections (#16)
* Update author names

* Update bibliography

Add papers that combine game theory and queueing theory

* Add initial draft of introduction

- First line (hook)
- Literature review methodology driven (game theory - queueing theory)
- Establish research problem
- Research objectives
- Map out the paper

* Cite papers on networks with tandem queues

* Remove unused citation

* Add some additional references

* Minor changes

- Remove unnecessary comments
- Apply suggestions based on alex and proselint
- Reference a paper on ED pressures
- Reference p

\section{EMS - ED application}

\subsection{Application}

@@

\begin{itemize}
    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
    receives
    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\in\{1, 2\}\)
    \item \( \mu_i \): The service rate of patients at ED \(i\in\{1, 2\}\)
    \item \( C_i \): The number of available resources (beds) in ED \(i\in\{1, 2\}\)  
    \item \( T_i \): The action that ED \(i\in\{1, 2\} \) chooses to play which 
    corresponds to the threshold at which they do not accept EMS patients.
    \item \( N_i \): The total patient capacity of ED \(i\in\{1, 2\} \)
    \item \( M_i \): The total parking capacity of ED \(i\in\{1, 2\} \)
    \item \( R \): The time target for both EDs
    \item \( \alpha \in [0, 1] \) : \textit{Weighting} of blocking time and 
    lost individuals (equation \ref{eq:obj_distributor})
\end{itemize}

The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system is within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the weighted combination of the ambulance blocking time and the percentage of 
lost ambulances is minimised. 
As defined in \ref{sec:model_overview}, the interaction between the two EDs 
is a Normal form game that is then used to inform the decision of the EMS.
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing (figure 
\ref{fig:imperfect_info_game}). This corresponds to reacting to experienced delays.

\subsection{Numerical Results}

This subsection aims to analyse how the gaming framework can affect the 
performance measures of the two hospitals and how to avoid certain inefficient 
situations.

The most commonly used method for analysing normal form games is the Nash 
equilibrium described in section \ref{sec:methodology_nash_equilibrium}
Consider the following game:

\begin{multicols}{3}
    \begin{itemize}
        \item \( \lambda_{1_1} \) = 1
        \item \( \mu_1 \) = 2
        \item \( C_1 \) = 2
        \item \( N_1 \) = 10
        \item \( M_1 \) = 6
        \columnbreak

        \item \( \lambda_{1_2} \) = 2
        \item \( \mu_2 \) = 2.5
        \item \( C_2 \) = 2
        \item \( N_2 \) = 10
        \item \( M_2 \) = 6
        \columnbreak

@@

The set of possible actions to choose from for player 1 and player 2 is the
set of thresholds that the EDs can choose from: 
\begin{equation}
    T_1 = \{ 0, \ldots, N_1 \}, \quad T_2 = \{ 0, \ldots, N_2 \}
\end{equation}

For this example the only Nash equilibrium of the game is achieved when both 
players choose a threshold of \( T_1 = 10, T_2 = 10 \).
This means that the two players' best response to each other is to only block
ambulances when they are full.

@@

The use of a learning algorithm allows to investigate, not only the outcome of 
the game, but also how that outcome is reached.
Consider figure \ref{fig:ard_by_itself}. 
By running asymmetric replicator dynamics on the system the behaviour that 
emerges can be observed.
It can be seen that for this particular set of parameters the strategies of 
the two hospitals converge over time. 
Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
the same strategy \(s_{10}\) which indicates that thresholds \(T_1 = 10\) and 
\(T_2 = 10\) are played.
What is more important in this example is how the two hospitals reached these
decisions which also highlights the importance of using a learning algorithm.
Hospital 2 is able to reach the decision in a short amount of time while 
hospital 1 takes longer and goes through numerous strategies to get there.

@@

Here, \(S\) is the set of all sets of strategies \((s_1, s_2)\), \(E\) is the 
set of all possible sets of equilibria and \(F\) is the cost function to 
measure the efficiency for.

To study the efficiency of the strategies being played a new concept is 
introduced that considers the ratio between each hospital's best achievable 
blocking time and the one that is being played.
This new concept is defined as the compartmentalised price of anarchy of the 
players of the game and is defined as \(PoA_i(\tilde{s})\), where 
\(i \in \{1, 2\}\) to distinguish among the two players/hospitals where 
\(\tilde{s}\) is the strategy that is being played by player \( i \). 
The compartmentalised price of anarchy aims to measure inefficiencies in the 
model.
The \(PoA\) for the blocking time of player \(i\) for strategy \(\tilde{s}\) 
is given by:

@@

\begin{multicols}{3}
    \begin{itemize}        
        \item \( \lambda_{1_1} \) = 4.5
        \item \( \mu_1 \) = 2
        \item \( C_1 \) = 3
        \item \( T_1 \in [1, N_1] \) 
        \item \( N_1 \) = 6
        \item \( M_1 \) = 5

        \columnbreak
        \item \( \lambda_{1_2} \) = 6
        \item \( \mu_2 \) = 3
        \item \( C_2 \) = 2
        \item \( T_2 \in [1, N_2] \)
        \item \( N_2 \) = 7
        \item \( M_2 \) = 4

@@

\textbf{Initial scenario:}
Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
dynamics the emergent behaviour can be measured and the compartmentalised price 
of anarchy at every iteration for both players.
Figure \ref{fig:ard_original} shows the strategies that are being played and 
the values of \(PoA_1(s)\) and \(PoA_2(s)\) for all iterations of the 
learning algorithm until it reaches an evolutionary stable pair of strategies.

@@

The learning algorithm reaches a stable pair of 
strategies where \(T_1 = 5\) and \(T_2 = 6\). After a number of iterations the
price of anarchy for both players stabilises and barely increases until the 
final iteration.

@@

By increasing \(\lambda_2\) there is no change as to how players behave
(\(T_1 = 5, T_2 = 6\)), but the efficiency of the system does change. 
There is a decline in the price of anarchy of the blocking time which at first 
glance indicates that upon flooding the system it becomes the loss in efficiency
due to rational individual behaviour decreases. 
This is non-sensical though.
What it really shows is that the steep increase in \( \lambda_2 \) leaves 
the system unable to cope regardless of the decisions made.

\textbf{Increasing number of servers \( C_1 \) and \( C_2 \):}
Figure \ref{fig:ard_num_of_servers} shows a run of asymmetric replicator 
dynamics with a change in the number of servers of the hospitals.
The number of servers are increased from \(C_1 = 3, C_2 = 2\) to 
\(C_1 = 4, C_2 = 3\).

@@

In this case, both the behaviour as well as the price of anarchy change.
The players change their strategies from \(T_1 = 5, T_2 = 6\) to 
\(T_1 = 6, T_2 = 7\) and the \(PoA\) of the blocking time goes down.
By adding more resources to the models they are able to increase their 
efficiency.
Although this is a good way to escape such inefficiencies, it might not always
be cost efficient.

@@

Figure \ref{fig:ard_penalty} shows that players start playing strategies 
\( T_1 = 5\) and \( T_2 = 6 \) and mid-run of the learning algorithm a penalty
is applied to these strategies on the payoff matrix.
By incentivising the players in such a way the players change their strategies 
to \(T_1 = 6\) and \(T_2 = 7\), and thus ambulance patients are accepted in the 
ED more often.
Hence, the \(PoA\) for both EDs is decreased, meaning that the whole system is
more efficient in terms of the blocking time.

>>>>

\section{EMS - ED application}\label{sec:ems_ed_application}

\subsection{Application}\label{sec:application}

@@

\begin{itemize}
    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
    receives and distributes to EDs
    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED 
    \(i\in\{A, B\}\)
    \item \( \mu_i \): The service rate of patients at ED \(i\in\{A, B\}\)
    \item \( C_i \): The number of available resources (beds) in ED 
    \(i\in\{A, B\}\)  
    \item \( T_i \): The action that ED \(i\in\{A, B\} \) chooses to play which 
    corresponds to the threshold at which they do not accept EMS patients.
    \item \( N_i \): The total patient capacity of ED \(i\in\{A, B\} \)
    \item \( M_i \): The total parking capacity of ED \(i\in\{A, B\} \)
    \item \( R \): The time target for both EDs
    \item \( \alpha \in [0, 1] \) : \textit{Weighting} of blocking time and 
    lost individuals (equation \ref{eq:obj_distributor})
\end{itemize}

The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system is within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the weighted combination of the ambulance blocking time and the percentage of 
lost ambulances is minimised. 
As defined in \ref{sec:model_overview}, the interaction between the two EDs 
is a normal form game that is then used to inform the decision of the EMS.
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing (figure 
\ref{fig:imperfect_info_game}). This corresponds to reacting to experienced 
delays.

\subsection{Numerical results}\label{sec:numerical_results}

This subsection aims to analyse how the gaming framework can affect the 
performance measures of the two hospitals and how to escape certain inefficient 
situations.

The most commonly used method for analysing normal form games is the Nash 
equilibrium described in section \ref{sec:methodology_nash_equilibrium}.
Consider the following game:

\begin{multicols}{3}
    \begin{itemize}
        \item \( \lambda_{1_A} \) = 1
        \item \( \mu_A \) = 2
        \item \( C_A \) = 2
        \item \( N_A \) = 10
        \item \( M_A \) = 6
        \columnbreak

        \item \( \lambda_{1_B} \) = 2
        \item \( \mu_B \) = 2.5
        \item \( C_B \) = 2
        \item \( N_B \) = 10
        \item \( M_B \) = 6
        \columnbreak

@@

The set of possible actions to choose from for player 1 and player 2 is the
set of thresholds that the EDs can choose from: 
\begin{equation}
    T_A \in [1, N_A], \quad T_B \in [1, N_B]
\end{equation}

For this example the only Nash equilibrium of the game is achieved when both 
players choose a threshold of \( T_A = 10, T_B = 10 \).
This means that the two players' best response to each other is to only block
ambulances when they are full.

@@

The use of a learning algorithm allows to investigate, not only the outcome of 
the game, but also how that outcome is reached.
Consider figure \ref{fig:ard_by_itself}. 
By running asymmetric replicator dynamics on the system the behaviour that 
emerges can be observed.
It can be seen that for this particular set of parameters the strategies of 
the two hospitals converge over time. 
Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
the same strategy \(s_{10}\) which indicates that thresholds \(T_A = 10\) and 
\(T_B = 10\) are played.
What is more important in this example is how the two hospitals reached these
decisions which also highlights the importance of using a learning algorithm.
Hospital 2 is able to reach the decision in a short amount of time while 
hospital 1 takes longer and goes through numerous strategies to get there.

@@

Here, \(S\) is the set of all sets of strategies \((s_A, s_B)\), \(E\) is the 
set of all possible sets of equilibria and \(F\) is the cost function to 
measure the efficiency for.

To study the efficiency of the strategies being played a new concept is 
introduced that considers the ratio between each hospital's best achievable 
blocking time and the one that is being played.
This new concept is defined as the compartmentalised price of anarchy of the 
players of the game and is defined as \(PoA_i(\tilde{s})\), where 
\(i \in \{A, B\}\) to distinguish among the two players/hospitals where 
\(\tilde{s}\) is the strategy that is being played by player \( i \). 
The compartmentalised price of anarchy aims to measure inefficiencies in the 
model.
The \(PoA\) for the blocking time of player \(i\) for strategy \(\tilde{s}\) 
is given by:

@@

\begin{multicols}{3}
    \begin{itemize}        
        \item \( \lambda_{1_A} \) = 4.5
        \item \( \mu_A \) = 2
        \item \( C_A \) = 3
        \item \( T_A \in [1, N_A] \) 
        \item \( N_A \) = 6
        \item \( M_A \) = 5

        \columnbreak
        \item \( \lambda_{1_B} \) = 6
        \item \( \mu_B \) = 3
        \item \( C_B \) = 2
        \item \( T_B \in [1, N_B] \)
        \item \( N_B \) = 7
        \item \( M_B \) = 4

@@

\textbf{Initial scenario:}
Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
dynamics the emergent behaviour can be measured and the compartmentalised price 
of anarchy at every iteration for both players.
Figure \ref{fig:ard_original} shows the strategies that are being played and 
the values of \(PoA_A(s)\) and \(PoA_B(s)\) for all iterations of the 
learning algorithm until it reaches an evolutionary stable pair of strategies.

@@

The learning algorithm reaches a stable pair of 
strategies where \(T_A = 5\) and \(T_B = 6\). After a number of iterations the
price of anarchy for both players stabilises and barely increases until the 
final iteration.

@@

By increasing \(\lambda_2\) there is no change as to how players behave
(\(T_A = 5, T_B = 6\)), but the efficiency of the system does change. 
There is a decline in the price of anarchy of the blocking time which at first 
glance indicates that upon flooding the system it becomes the loss in efficiency
due to rational individual behaviour decreases. 
This is non-sensical though.
What it really shows is that the steep increase in \( \lambda_2 \) leaves 
the system unable to cope regardless of the decisions made.

\textbf{Increasing number of servers \( C_A \) and \( C_B \):}
Figure \ref{fig:ard_num_of_servers} shows a run of asymmetric replicator 
dynamics with a change in the number of servers of the hospitals.
The number of servers are increased from \(C_A = 3, C_B = 2\) to 
\(C_A = 4, C_B = 3\).

@@

In this case, both the behaviour as well as the price of anarchy change.
The players change their strategies from \(T_A = 5, T_B = 6\) to 
\(T_A = 6, T_B = 7\) and the \(PoA\) of the blocking time goes down.
By adding more resources to the models they are able to increase their 
efficiency.
Although this is a good way to escape such inefficiencies, it might not always
be cost efficient.

@@

Figure \ref{fig:ard_penalty} shows that players start playing strategies 
\( T_A = 5\) and \( T_B = 6 \) and mid-run of the learning algorithm a penalty
is applied to these strategies on the payoff matrix.
By incentivising the players in such a way the players change their strategies 
to \(T_A = 6\) and \(T_B = 7\), and thus ambulance patients are accepted in the 
ED more often.
Hence, the \(PoA\) for both EDs is decreased, meaning that the whole system is
more efficient in terms of the blocking time.

### 2021-11-02 sections/methodology/main.tex
Changes based on self review
I just read the whole thing and made some minor
changes here and there.

Th problem defined in section \ref{sec:model_overview} describes a normal-form
game between the decision makers of two queueing systems and a third player that 
decides how to distribute individuals to the systems.
The strategy space of the two queueing systems is defined as the possible values
that the threshold parameter can take \(T_i \in (1, N_i)\).
Then, the distributor has to decide on the proportion of individuals to send to 
each queueing system \(p_A \text{ and } p_B\), where \(p_A, p_B \in [0, 1] \)
and \(p_A + p_B = 1\).
Figure \ref{fig:imperfect_info_game} form section \ref{sec:model_overview} 
shows a diagrammatic representation of the game to be played and the decisions 
to be made.
As described in section \ref{sec:model_overview} queueing system \(A\) decides
on a strategy, at the same time, queueing system \(B\) chooses its own 
threshold, unaware of the first queueing system's choice.
Finally, the distributor makes its choice based on the strategies that the 
queueing systems chose to play.

@@

\subsection{Backwards Induction}

@@

These are the utilities of players \(A\) and \(B\) when both players choose a
strategy of \(T = 1\).
Here \(R\) is the predefined waiting time target to be met by a percentage of 
individuals \( \hat{P} \) and \(P(W_i < t)\) is properly defined in section
\ref{sec:proportion_within_target}.

@@

\subsection{Nash Equilibrium}\label{sec:methodology_nash_equilibrium}

@@

Computation of Nash equilibria can be done relatively efficiently using the 
Lemke Howson algorithm~\cite{LemkeHowson}.
Lemke-Howson uses best response polytopes to get one of the Nash equilibrium of
the game. 
Other algorithms exists that will compute all Nash equilibria but 
for large games the computational complexity becomes problematic.
All game theoretic calculations were done in Python using the Nashpy library 
\cite{thenashpyproject}.

\subsection{Learning Algorithms}\label{sec:methodology_learning_algorithms}

>>>>

Th problem defined in section \ref{sec:model_overview} describes a normal-form
game between the decision makers of two queueing systems and a third player that 
decides how to distribute individuals to the systems.
The strategy space of the two queueing systems is defined as the possible values
that the threshold parameter can take \(T_i \in [1, N_i]\).
Then, the distributor has to decide on the proportion of individuals to send to 
each queueing system \(p_A \text{ and } p_B\), where \(p_A, p_B \in [0, 1] \)
and \(p_A + p_B = 1\).
Figure \ref{fig:imperfect_info_game} form section \ref{sec:model_overview} 
shows a diagrammatic representation of the game to be played and the decisions 
to be made.
As described in section \ref{sec:model_overview} queueing system \(A\) decides
on a strategy, at the same time, queueing system \(B\) chooses its own 
threshold, unaware of the first queueing system's choice.
Finally, the distributor makes its choice based on the strategies that the 
queueing systems chose to play.

@@

\subsection{Backwards induction}

@@

These are the utilities of players \(A\) and \(B\) when both players choose a
strategy of \(T = 1\).
Here \(R\) is the predefined waiting time target to be met by a percentage of 
individuals \( \hat{P} \) and \(P(W_i < t)\) is defined in section
\ref{sec:proportion_within_target}.

@@

\subsection{Nash equilibrium}\label{sec:methodology_nash_equilibrium}

@@

Computation of Nash equilibria can be done in a relatively efficient way using 
the Lemke Howson algorithm~\cite{LemkeHowson}.
Lemke-Howson uses best response polytopes to get one of the Nash equilibrium of
the game. 
Other algorithms exists that will compute all Nash equilibria but 
for large games the computational complexity becomes problematic.
All game theoretic calculations were done in Python using the Nashpy library 
\cite{thenashpyproject}.

\subsection{Learning algorithms}\label{sec:methodology_learning_algorithms}

### 2021-11-02 sections/model_overview/main.tex
Minor changes on waiting zones
- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones
Changes based on self review
I just read the whole thing and made some minor
changes here and there.

The queueing systems are designed in such a way where they can accept two types
of individuals. 
These are the individuals that the distributor allocates to them and 
other individuals from other sources. 
Each queueing system may then choose to block the individuals that arrive from 
the distributor when the system reaches a certain capacity. 
The strategy sets for each queueing system is the set 
\( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
the total capacities of the two queueing systems. We denote the chosen actions 
from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.

@@

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[>=stealth, scale=0.8],
        % the rectangle of Queue 1
        \draw (0,0) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
        % The label above Queue 1 -> M
        \node[anchor=north] at (1.5cm, 1cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{M} 
        \)};
        % the vertical lines in Queue 1
        \foreach \i in {1,...,4, 5.7}
        \draw (2cm-\i*10pt,0) -- +(0,-1.5cm);

        % the circle in Queue 1
        \draw (2.75,-0.75cm) circle [radius=0.75cm] node {\(0\)};

@@

        % The label above Queue 2 -> N
        \node[anchor=north] at (6.6cm, 2.2cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{N} 
        \)};

@@

        % Line from lambda_2 to Queue 1
        \draw[<-] (-0.3,-0.75) -- +(-40pt,0) node[left] {\( \lambda_2 \)};
        % First line (horizontal) after Queue 1
        \draw[-] (3.5,-0.75) -- +(20pt,0);
        % Second line (vertical) after Queue 1
        \draw (4.2, 0.525) -- (4.2, -0.75);

@@

where \(W\) is the mean waiting time of all individuals, \(t\) is the time 
target and \(\hat{P}\) is the percentage of individuals need to be within that 
target. 
There are numerous objective functions that can be used to capture this 
behaviour. 
For example one approach is to use the threshold that maximises the probability 
that 
the mean waiting is more than the target time, and completely ignore the 
percentage goal.

@@

The third player, the distributor has their own choices to make and their own 
goals to satisfy.
The strategy set of the third player is the proportion \(0 \leq p_A \leq 1\) of 
individuals it sends to the first queueing system (the proportion 
\(p_B = 1 - p_A\) is sent to the second queueing system).
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals (\(B_i\))
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distributor is the proportion of lost individuals (\(L_i\)).
Equation \ref{eq:obj_distributor} can be used to capture a mixture 
between the two objectives \(L_i\) and \(B_i\) where \(i \in \{A, B\}\).
\begin{equation*}\label{eq:obj_distributor}
    (p_A, p_B) \quad s.t. \quad 
    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
\end{equation*}

@@

Using equations (\ref{eq:obj_queueing_systems}) and (\ref{eq:obj_distributor}) 
gives an imperfect information extensive form game. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players~\cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each of the first two players chooses to play.
In other words, each queueing system chooses to play a strategy without 
knowing the other system's strategy.
The distributor then, fully aware of the chosen threshold strategies, distributes 
individuals among the two systems in order to minimise the time that its 
individuals will be blocked. Figure \ref{fig:imperfect_info_game} illustrates this.

@@

\begin{equation} \label{eq:payoff_entry}
    U_{T_1, T_2}^i = -\left( 
        \hat{P} - P(W_i < t) 
    \right)^2 \quad \textbf{where } i \in \{A, B\}
\end{equation}

>>>>

The queueing systems are designed in such a way where they can accept two types
of individuals. 
These are the individuals that are allocated by the distributor and 
other individuals from other sources. 
Each queueing system may then choose to block the individuals that arrive from 
the distributor when the system reaches a certain capacity. 
The strategy sets for each queueing system is the set 
\( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
the total capacities of the two queueing systems. We denote the chosen actions 
from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.

@@

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[>=stealth, scale=0.8],
        % the rectangle of Queue 1
        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
        % The label above Queue 1 -> M
        \node[anchor=north] at (1.5cm, 1cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{M} 
        \)};
        % The label below Queue 1 -> Waiting zone 2
        \node[anchor=north] at (1.5cm, -1.7cm) {\small{Waiting zone 2}};

        % the vertical lines in Queue 1
        \foreach \i in {1,...,5, 6.6}
        \draw (3cm-\i*13pt,0) -- +(0,-1.5cm);

        % % the circle in Queue 1
        % \draw (2.75,-0.75cm) circle [radius=0.75cm] node {\(0\)};

@@

        % The label above Queue 2 -> N
        \node[anchor=north] at (6.6cm, 2.2cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{N} 
        \)};
        % The label below Queue 2 -> Waiting zone 1
        \node[anchor=north] at (6.2cm, -0.5cm) {\small{Waiting zone 1}};

@@

        % Line from lambda_2 to Queue 1
        \draw[<-] (-0.3,-0.75) -- +(-40pt,0) node[left] {\( \lambda_2 \)};
        % First line (horizontal) after Queue 1
        \draw[-] (3,-0.75) -- +(34pt,0);
        % Second line (vertical) after Queue 1
        \draw (4.2, 0.525) -- (4.2, -0.75);

@@

where \(W\) is the waiting time of a potential individual, \(t\) is the time 
target and \(\hat{P}\) is the percentage of individuals need to be within that 
target. 
There are numerous objective functions that can be used to capture this 
behaviour. 
For example one approach is to use the threshold that maximises the probability 
that 
the mean waiting is more than the target time, and completely ignore the 
percentage goal.

@@

The third player, the distributor, has their own choices to make and their own 
goals to satisfy.
The strategy set of the third player is the proportion \(0 \leq p_A \leq 1\) of 
individuals it sends to the first queueing system (the proportion 
\(p_B = 1 - p_A\) is sent to the second queueing system).
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals (\(B_i\))
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distributor is the proportion of lost individuals (\(L_i\)).
Equation \ref{eq:obj_distributor} can be used to capture a mixture 
between the two objectives \(L_i\) and \(B_i\) where \(i \in \{A, B\}\).
\begin{equation*}\label{eq:obj_distributor}
    (p_A, p_B) \quad s.t. \quad 
    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
\end{equation*}

@@

Using either equation (\ref{eq:obj_queueing_systems}) or equation
(\ref{eq:obj_distributor}) gives an imperfect information extensive form game. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players~\cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each of the first two players chooses to play.
In other words, each queueing system chooses to play a strategy without 
knowing the other system's strategy.
The distributor then, fully aware of the chosen threshold strategies, 
distributes individuals among the two systems in order to minimise the time 
that its individuals will be blocked. Figure \ref{fig:imperfect_info_game} 
illustrates this.

@@

\begin{equation} \label{eq:payoff_entry}
    U_{T_A, T_B}^i = -\left( 
        \hat{P} - P(W_i < t) 
    \right)^2 \quad \textbf{where } i \in \{A, B\}
\end{equation}

### 2021-11-02 sections/queueing_model/main.tex
Changes to Methodology and Model overview sections
- Chnages in some notation
- Define expressions only once and then just reference them
- Changes in some labels (including some more sections)
- Other minor rewordings
Minor changes on waiting zones
- Display waiting zones 1 and 2 on the queueing system
- Fix some text that listed the incorrect waiting zones
Changes based on self review
I just read the whole thing and made some minor
changes here and there.

The model consists of two types of individuals; type 1 and type 2.
Type 1 individuals arrive instantly at waiting zone 1 and proceed to wait to
receive their service. 
Type 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed only when the number of 
individuals in waiting zone 1 \textbf{and} in service is less than a 
pre-determined threshold \(T\).
When the number of individuals is equal to or exceeds this threshold, all 
second type individuals that arrive will stay 
\textit{``blocked''} in waiting zone 1 until the number of people in the 
system is reduced below \(T\). 
This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

@@

The transition matrix \(Q\) of the Markov chain consists of the transition rates
between the numerous states of the model. Every entry \( Q_{ij} = 
Q_{(u_i, v_i),(u_j, v_j)} \) represents the transition rate from state 
\( i = (u_i, v_i) \) to state \( j = (u_j , v_j) \) for all 
\( (u_i, v_i), (u_j, v_j) \in S \).
The entries of \(Q\) can be calculated using the state-mapping function 
described in (\ref{eq:markov_transition_rate}):

@@

Note that \(\Lambda\) here denotes the overall arrival rate in the model by both 
types of individuals (i.e. \(\Lambda = \lambda_1 + \lambda_2\)). 
A visualisation of how the transition rates relate to the states of the model 
can be seen in the general Markov chain model shown in figure 
\ref{fig:general-markov-model}.

@@

The transition matrix \( Q \) defined in (\ref{eq:markov_transition_rate}) can 
be used to get the probability vector \( \pi \).
The vector \( \pi \) is commonly used to study stochastic systems and it's main
purpose is to keep track of the probability of being at any given state of 
the system. 
\(\pi_i\) is the steady state probability of being in state \((u_i, v_i) \in 
\tilde S\) which is the \(i^{\text{th}}\) state of \(\tilde S\) for some ordering of 
\(\tilde S\).
The term \textit{steady state} refers to the instance of the vector \( \pi \) 
where the probabilities of being at any state become stable over time. 
Thus, by considering the steady state vector \( \pi \) the relationship between 
it and \( Q \) is given by:

@@

Consequently, there are some additional performance measures of interest that
are not as straightforward to calculate.
Such performance measures are the mean waiting time in the system (for both 
type 1 and type 2 individuals), the mean time blocked in waiting zone 2 (only 
valid for type 2 individuals) and the proportion of individuals that wait in 
waiting zone 1 within a predefined time target.

>>>>

The model consists of two types of individuals; type 1 and type 2.
Type 1 individuals arrive instantly at waiting zone 1 and wait to receive their 
service. 
Type 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed only when the number of 
individuals in waiting zone 1 \textbf{and} in service is less than a 
pre-determined threshold \(T\).
When the number of individuals is equal to or exceeds this threshold, all 
second type individuals that arrive will stay 
\textit{``blocked''} in waiting zone 2 until the number of people in 
the next queue and in service falls below \(T\). 
This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

@@

The generator matrix \(Q\) of the Markov chain consists of the 
rates between the numerous states of the model. 
Every entry \( Q_{ij} = Q_{(u_i, v_i),(u_j, v_j)} \) represents the rate from 
state \( i = (u_i, v_i) \) to state \( j = (u_j , v_j) \) for all 
\( (u_i, v_i), (u_j, v_j) \in S \).
The entries of \(Q\) can be calculated using the state-mapping function 
described in (\ref{eq:markov_transition_rate}):

@@

Note that \(\Lambda\) here denotes the overall arrival rate in the model by both 
types of individuals (i.e. \(\Lambda = \lambda_1 + \lambda_2\)). 
A visualisation of how the transition rates relate to the states of the model 
can be seen in the general Markov chain model shown in figure 
\ref{fig:general_markov_model}.

@@

The generator matrix \( Q \) defined in (\ref{eq:markov_transition_rate}) can 
be used to get the probability vector \( \pi \).
The vector \( \pi \) is commonly used to study stochastic systems and it's main
purpose is to keep track of the probability of being at any given state of 
the system. 
\(\pi_i\) is the steady state probability of being in state \((u_i, v_i) \in 
\tilde S\) which is the \(i^{\text{th}}\) state of \(\tilde S\) for some ordering of 
\(\tilde S\).
The term \textit{steady state} refers to the instance of the vector \( \pi \) 
where the probabilities of being at any state become stable over time. 
Thus, by considering the steady state vector \( \pi \) the relationship between 
it and \( Q \) is given by:

@@

Consequently, there are some additional performance measures of interest that
are not as straightforward to calculate.
Such performance measures are the mean waiting time in the system (for both 
type 1 and type 2 individuals), the mean time blocked in waiting zone 2 (only 
valid for type 2 individuals) and the proportion of individuals that wait in 
waiting zone 1 within a predefined time target (for both types).
